Truthfulness Verification System

### 2011-04-13 trunk/proposal/paper.tex
Added concluding remark

\subsubsection{Sullivan is the fastest swimmer in the world}
The alternative units for this sentence are "Sullivan", "Michael phelps", "ALexander", "Long", and "Ernest". Similar to the previous sentence, the algorithm 2 can not produce good ranking for for this sentence. However, our algorithm 1 produces correct ranking and together they produce overall correct result

>>>>

\subsubsection{Sullivan is the fastest swimmer in the world}
The alternative units for this sentence are "Sullivan", "Michael phelps", "ALexander", "Long", and "Ernest". Similar to the previous sentence, the algorithm 2 can not produce good ranking for for this sentence. However, our algorithm 1 produces correct ranking and together they produce overall correct result.

\section{Conclusion}
This ranking procedure bolsters the result in the previous algorithm always without any exception. On observing the five examples above, we expect a combination of the two algorithms will give us a proper ranking of the alternate units for proper truth verification.
